---
title: "LAB3"
author: "YunranChen"
date: "1/30/2019"
output: 
  ioslides_presentation:
    widescreen: true
    smaller: true
---

<style>
slides > slide {
  overflow-x: auto !important;
  overflow-y: auto !important;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


## Outline

- R package `igraph` 
    - Paths
        - Paths, distances and diameter
        - Components
        - Transitivity and reciprocity
        - Max-flow and min-cut
    - Communities
        - Pre-defined clusters
        - Different algorithms
    - Visualization
        - Color the paths
        - Plotting clusters
        - Plotting dendrograms
        - Mark groups
    
## `igraph`

- Official website (handbook): <http://igraph.org/r/>
- Book: <https://sites.fas.harvard.edu/~airoldi/pub/books/BookDraft-CsardiNepuszAiroldi2016.pdf>


## Preparation

```{r install, echo=TRUE, message=FALSE, warning=FALSE}
library(igraph)
library(igraphdata)
data(USairports)
data(karate)
```

```{r,echo=TRUE}
?USairports
?karate
```

## Preprocess

```{r,echo=TRUE}
USairports
#should have no self-loop
sum(which_loop(USairports))
USairports <- simplify(USairports, remove.loops = TRUE, remove.multiple = FALSE)
sum(which_loop(USairports))
#different carrier and aircraft types leading to multiple graphs
USairports[["RDU","JFK",edges=TRUE]][[1]][[1:5]]
#simplify
air <- simplify(USairports, edge.attr.comb =list(Departures = "sum", Seats = "sum", Passengers = "sum",Distance="mean", "ignore"))
air
air[["RDU","JFK",edges=TRUE]]
```


# Paths

## Paths, distances and diameter


##  Select specific paths

Select specific paths

```{r,echo=TRUE}
#select length 1 path
air[[from="RDU",to="BOS",edges=TRUE]]

# select >=1 paths
flight_rdu_bos=V(air)["RDU","JFK","BOS"]
E(air,path=flight_rdu_bos)

#another way
E(air)["RDU"%->%"JFK","JFK"%->%"BOS"]

```


## Shortest paths

Many paths between edges. Direct flight or multiple steps.

Length of path: number of edges included in a path

`shortest_paths`: only one of the shortest paths

`all_shortest_paths`: all the shortest paths; `nrgeo` is the resultant vector of values from Djikstra's algorithm which is used to find the shortest paths. 

```{r,echo=TRUE}
#arkansas airport-XNA
shortest_paths(air,from="RDU",to = "XNA",weights = E(air)$Distance)$vpath
shortest_paths(air,from="RDU",to = "XNA",weights = NA)$vpath #one of the shortest path
shortest_paths(air,from="RDU",to = "XNA",mode = "in",weights = NA)$vpath #to
shortest_paths(air,from="RDU",to = "XNA",mode = "out",weights = NA)$vpath #from
shortest_paths(air,from="RDU",to = "XNA",mode = "all",weights = NA)$vpath #undirected

all_shortest_paths(air,from="RDU",to = "XNA",weight=NA)$res
all_shortest_paths(air,from="RDU",to = "XNA",weights = E(air)$Distance)$res

```

## Color certain paths:

Color the path from `Actor 33` to `Mr Hi` and set the width for the path.

```{r,echo=TRUE}
path_vk=shortest_paths(karate,from="Actor 33", to="Mr Hi")$vpath[[1]]
ecol=rep("gray80",ecount(karate))
ecol[E(karate,path = path_vk)]="orange"
ew=rep(1,ecount(karate))
ew[E(karate,path = path_vk)]=3
plot(karate,edge.color=ecol,edge.width=ew)
```


## distance

Distance: length of shortest path

`distance_table`: The frequency of shortest path length between each pair of vertices.

```{r,echo=TRUE}
distance_table(air)
# unconnected: the number of pairs for which the first vertex is not reachable from the second
```

---

`distances`

```{r,echo=TRUE}
distances(air,"RDU","XNA",weights = NA) # not consider the weight

distances(air,"RDU","XNA",weights =  E(air)$Distance) # specify the weight
# how the function `distances` works
(shortest_paths(air,from="RDU",to = "XNA",weights = E(air)$Distance)$vpath[[1]])
E(air)["RDU"%->%"CLT","CLT"%->%"XNA"]$Distance%>%sum()

#can return a distance matrix
distances(air,c("BOS","JFK","RDU","XNA"),c("BOS","JFK","RDU","XNA"),weights = E(air)$Distance,mode = "all") #undirected
distances(air,c("BOS","JFK","RDU","XNA"),c("BOS","JFK","RDU","XNA"),weights = E(air)$Distance,mode = "in") #focus on to
distances(air,c("BOS","JFK","RDU","XNA"),c("BOS","JFK","RDU","XNA"),weights = E(air)$Distance,mode = "out") #focus on from # tranpose of mode "in"

```

---

`mean_distance`:  average path length in a graph, by calculating the shortest paths between **all** pairs of vertices (both ways for directed graphs). **does not consider edge weights currently** and uses a breadth-first search.

```{r,echo=TRUE}
# connected=TRUE
mean_distance(air,directed = TRUE)
# How the function works
freq=distance_table(air)$res/sum(distance_table(air)$res)
sum(freq*1:9)

#connected=FALSE
mean_distance(air,directed = TRUE,unconnected = FALSE)
#How the function works
freq=c(distance_table(air)$res,distance_table(air)$unconnected)/sum(c(distance_table(air)$res,distance_table(air)$unconnected))
sum(freq*c(1:9,vcount(air)))
```


## Diameter

diameter: The largest distance of a graph. In the special case when some vertices are not reachable via a path from some others, returns the longest finite distance.

```{r,echo=TRUE}
diameter(air)
diameter(air,weights = E(air)$Distance)
diameter(air,directed = FALSE)
#can also specify the unconnected=TRUE/FALSE
```

## Get the nodes and edges of the airports in the longest path

```{r,echo=TRUE}
#get the nodes
get_diameter(air,weights = E(air)$Distance)
dia_v=get_diameter(air,weights = E(air)$Distance)
# information of nodes
dia_v[[]]
# edges
E(air,path = dia_v)
# info of edges
dia_e=E(air,path = dia_v)
dia_e[[]]

## delete the flight with passengers <= 10 then recalculate the diameter

air_filt=delete_edges(air,E(air)[Passengers<=10])
get_diameter(air_filt,weights = E(air_filt)$Distance)

```

## Color the paths along the diameter

First step is to select the edges along the path. 

Then just change the edge attribute.

```{r,echo=TRUE}
dia_vk=get_diameter(karate,directed = FALSE)
ecol=rep("gray80",ecount(karate))
ecol[E(karate,path = dia_vk)]="orange"
plot(karate,edge.color=ecol)
```


# Components

## Components

For an undirected graph,

Connected: if there is a path from any vertex to any other.

Unconnected: if not connected. An unconnected graph has multiple components.

Components: a maximal induced subgraph that is connected.

```{r,echo=TRUE}
is_connected(air)
count_components(air)
#no:number of components
names(igraph::components(air))
igraph::components(air)$csize
igraph::components(air)$membership[igraph::components(air)$membership==6]
# check whether RDU is in the largest component
subcomponent(air,"RDU") #not bad
```

## strongly connected and weakly connected

For a directed network,

weakly connected: its corresponding undirected network that ignored edge directions, is connected

strongly connected: if and only if it has a directed path from each vertex to all other vertices.

```{r,echo=TRUE}
is_connected(air,mode = "weak")
is_connected(air,mode = "strong")
count_components(air,mode = "strong")
igraph::components(air,mode = "strong")$membership%>%table()
# check whether RDU is in the largest component
"RDU"%in%(igraph::components(air,mode = "strong")$membership[igraph::components(air,mode = "strong")$membership==25]%>%names()) # not bad
```

## Transitivity and reciprocity 

Network and node properties 

## Reciprocity

The proportion of reciprocated ties for a directed network

```{r,echo=TRUE}
#number of reciprocity edges divided by number of edges
reciprocity(air)
2*dyad_census(air)$mut/ecount(air) 
# number of mutual pairs divided by number of connected pairs
reciprocity(air,mode = "ratio")
dyad_census(air)$mut/(dyad_census(air)$mut+dyad_census(air)$asym)

#number of pairs
dyad_census(air)
```

## transitivity

global: ratio of triangles to connected triples.

local: ratio of triangles to connected triples each vertex is part of.

```{r,echo=TRUE}
transitivity(air,type = "global")
transitivity(air,type = "local")[1:5]
transitivity(air,vids = c("RDU","JFK"),type = "local") # specify multiple vertices

#corresponds to different types of triples
triad_census(air)

?triad_census
```


## maximum flows and minimum cuts

max flow How many passengers the US airport network can transport from a given airport to another one.

```{r,echo=TRUE}
E(air)[["BOS"%->%"JFK"]]
# use seat to present the capacity.
max_flow(air,"BOS","JFK",capacity = E(air)$Seats)$value
#capacity is for max_flow() function as default
E(air)$capacity=E(air)$Seats
max_flow(air,"BOS","JFK")$value

```

## maximum flows and minimum cuts

min cut: the minimum **number of edges**, that disconnect a destination vertex from a departure vertex. In a **weighted** network with edge capacities the minimum cut calculates the **total capacity** needed to disconnect the vertex pair.

```{r,echo=TRUE}
E(air)[["BOS"%->%"JFK"]]
# use seat to present the capacity.
min_cut(air,"BOS","JFK",capacity = E(air)$Seats)
#capacity is for max_flow() function as default
E(air)$capacity=E(air)$Seats
min_cut(air,"BOS","JFK")

```

## maximum flows and minimum cuts

max-flow min-cut theorem: the minimum cut in a graph from a source vertex to a target vertex always **equals** the maximum flow between the same vertices.

```{r,echo=TRUE}
min_cut(air,"BOS","JFK",capacity = E(air)$Seats)
max_flow(air,"BOS","JFK",capacity = E(air)$Seats)$value
```

# Community

## Make clusters

You can speicfy the cluster as you want.

```{r,echo=TRUE}
data("karate")

#ground truth
V(karate)$Faction
ground_truth=make_clusters(karate,V(karate)$Faction)
ground_truth

#cluster by the distance
dist_memb=karate %>%
distances(v = c("John A", "Mr Hi")) %>% 
  apply(2, which.min) %>%
make_clusters(graph = karate)

```

## Community detection

Different algorithm for community detection (clustering)

## Girvan-Newman algorithm 

Girvan-Newman algorithm (edge betweenness method): the number of shortest paths passing through an intra-community edge should be low while inter-community edges are likely to act as bottlenecks that participate in many shortest paths between vertices of different communities.

```{r,echo=TRUE}
dendrogram <- cluster_edge_betweenness(karate)
dendrogram
plot_dendrogram(dendrogram) # for hierarchical structure
membership(dendrogram) # best cut in terms of modularity
cut_at(dendrogram,no = 2) # cut into two groups
V(karate)[Faction == 1]$shape <- "circle"
V(karate)[Faction == 2]$shape <- "square"
set.seed(1)
plot(dendrogram,karate)
```

## Exact modularity maximization

Exact modularity maximization: optimization problem to maximum the modularity

```{r,echo=TRUE}
optimal=cluster_optimal(karate)
set.seed(1)
plot(optimal,karate)
optimal_lg=cluster_fast_greedy(karate)
set.seed(1)
plot(optimal,karate)
```

## Leading eigenvector

```{r,echo=TRUE}
eigen=cluster_leading_eigen(karate)
set.seed(1)
plot(eigen,karate)
clusters <- cluster_leading_eigen(karate, steps = 1) #at most two cluster


```

## Label propagation algorithm: 

The algorithm terminates when it holds for each node that it belongs to a community to which a maximum number of its neighbors also belong.

`fixed`: TRUE-label will not change.
`initial`: initial point.

```{r,echo=TRUE}

#non-negative values: different labels; negative values: no labels
initial=rep(-1,vcount(karate))
fixed=rep(FALSE,vcount(karate))
#need to have names
names(initial)=names(fixed)=V(karate)$name 
initial['Mr Hi']=1
initial['John A']=2
fixed['Mr Hi']=fixed['John A']=TRUE
lab=cluster_label_prop(karate,initial = initial,fixed = fixed)
set.seed(1)
plot(lab,karate)
set.seed(1)
plot(ground_truth,karate)
```


## Other algorithms:

`cluster_spinglass`

...

# Visualization 

## Visulization 

- color the paths
- plotting clusters
- plotting dendrograms
- marked several grouping vertices

`plot` support `igraph` and other igraph objects such as `vertexclustering`, `vertexdendrogram`, ... 


## Plotting clusters

`plot(vertexdendrogram,igraph)`

```{r,echo=TRUE}
set.seed(1)
plot(ground_truth,karate)
```


## Plotting dendrograms

`plot_dendrogram(vertexdendrogram)`

Not flexible enough. Try `ggdendrogram()` in `ggplot2` package.

```{r,echo=TRUE}
set.seed(1)
plot_dendrogram(dendrogram)
#labels at the same height: hang=-1
#cex: size of labels
plot_dendrogram(dendrogram,hang = -1, cex = 0.6) 
```

## marked groups

`plot`:

- `mark.group`: list
- `mark.col`: vector
- `mark.border`: vector
- `mark.shape`: vector (smoothness of the border, range from -1 to 1)
- `mark.expand`: vector (size of the border)

```{r,echo=TRUE}
ls=list(`1`=ground_truth[[1]],`2`=ground_truth[[2]])
ls
# other pars can be set as default
set.seed(1)
plot(karate,mark.groups = ls)

set.seed(1)
plot(karate,mark.groups = ls,mark.col = c("lightblue","yellow"),mark.border = rainbow(length(ls),alpha=1),mark.shape=c(-0.5,1),mark.expand = 1:2)

```

# More about `igraph`

## More about `igraph`

- Epidemics on networks: compartmental models on netwoks
- Spectral embeddings: community detection
- Change-point detection in temporal graphs
- CLustering multiple graphs
- Cliques and graphlets
- Graphons
- Graph matching

