---
title: "LAB7"
author: "YunranChen"
date: "2/28/2019"
output: 
  ioslides_presentation:
    widescreen: true
    smaller: true
---

<style>
slides > slide {
  overflow-x: auto !important;
  overflow-y: auto !important;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


## Outline

**Web APIs:**

Web APIs (application programming interface): website offers a set of structured http requests that return JSON or XML files.

- R packages: `rtweet` (twitter), `Rfacebook` (facebook), `RedditExtractoR` (reddit), `imdbapi` (IMDB), `omdbapi`(The Open Movie Database).

- API request from R. `rjson` (map JSON file to datafram),`rvest` (web scrapping).


**Twitter API**

- Retweet networks
- Friendship networks


- API authorization
- API request
- Creating networks based on datasets (Retweet networks)
- **Multiple requests based on results (Friendship networks)**


## Preparation

```{r install, echo=TRUE, message=FALSE, warning=FALSE}
#install.packages("rtweet")
library("rtweet")
library(dplyr)
library(igraph)
library(purrr)
library("stringr")
```

## Retweet networks

```{r,cache=TRUE,echo=TRUE}
rt_duke <- search_tweets(
  "#duke", n = 1000
)
nrow(rt_duke)
names(rt_duke)

netdf=rt_duke%>%dplyr::select(.,screen_name,retweet_screen_name,is_retweet)
netdfr=netdf%>%filter(is_retweet)%>%select(-is_retweet)
netdfp=netdf%>%filter(!is_retweet)%>%pull(screen_name)
igra_duke=graph_from_data_frame(netdfr)#+netdfp
E(igra_duke)$weight=rep(1,ecount(igra_duke))
igra_duke_s <- igraph::simplify( igra_duke, remove.multiple = T, remove.loops = F, 
                 edge.attr.comb=c(weight="sum"))
igra_duke_s
plot(igra_duke_s,vertex.color="gold", vertex.size=log(degree(igra_duke_s))*3+1, 
     vertex.frame.color="gray", vertex.label.color="black", 
     vertex.label.cex=log(degree(igra_duke_s))*0.2+0.1, vertex.label.dist=2, edge.curved=0.5,edge.arrow.size=.2)
```

# Friendship networks

## Friendship networks

Friendship network of NYC political science

directed: following

`get_friends()`: Get user IDs of accounts followed by target user(s).

```{r,echo=TRUE,cache=TRUE}
##maximum ids: 100
user.seed="drewconway"
user.following=get_friends(user.seed,n=500,retryonratelimit = TRUE)
nrow(user.following)
user.following%>%head(5)

```

## filter on the following user list

```{r,echo=TRUE,cache=TRUE}
info.following=lookup_users(user.following$user_id)
info.following
names(info.following)
##choose the filtering criterion: description, verified (blue check mark), location
info.following%>%select(geo_coords,country,country_code,location)%>%lat_lng()
## filter based on description
candidates=info.following%>%filter(description%>%
                          str_detect("nyu|new york university"),
                        description%>%
                          str_detect("poli(tics|tical|sci|cy)"))%>%
  select(user_id,screen_name,name,friends_count,description)
candidates%>%head(5)
```

## request rate limit

`rate_limit`

<https://developer.twitter.com/en/docs/developer-utilities/rate-limit-status/api-reference/get-application-rate_limit_status>


```{r,echo=TRUE,cache=TRUE}
rate_limit()%>%head()
rate_limit("get_friends")
get_friends(c("drewconway","BarackObama"))
rate_limit("get_friends") # 15 every 15 min
rate_limit("lookup_users") # 900 every 15 min
```


```{r,echo=TRUE,cache=TRUE,eval=FALSE}
limit.fri=rate_limit("get_friends")
  if (limit.fri$remaining==0){
    Sys.sleep(60*as.numeric(limit.fri$reset))}
```

## Friendship network 

```{r,echo=TRUE,cache=TRUE,eval=FALSE}
# seed user
user.seed= 20916144 #"cdsamii"
user.following=get_friends(user.seed,n=15,retryonratelimit = TRUE)
userid=c(user.seed,user.following$user_id)
info.following=lookup_users(userid)
user.df=info.following%>%filter(description%>%
                          str_detect(regex("nyu|new york university",ignore_case = T)),
                        description%>%
                          str_detect(regex("poli(tics|tical|sci|cy)",ignore_case = T))
                        )%>%
  select(user_id,screen_name,name,friends_count,description)
acc.id=user.df$user_id # qualified id
nyc.id=user.seed # already scrapped the friends
can.id=acc.id[!acc.id%in%nyc.id] # to be scrapped
rej.id=userid[!info.following$user_id%in%acc.id] # non-qualified
edge.list=user.following%>%filter(user_id%in%acc.id) # netowork
info.id=userid # already request user info
while((length(nyc.id)<100)){
  # pick the first user in the acc.id
user.following=get_friends(can.id,n=1000,retryonratelimit = TRUE)
userid=user.following$user_id
useridx=userid[!userid%in%info.id] # new userid
info.following=lookup_users(useridx)
user.dfx=info.following%>%filter(description%>%
                          str_detect(regex("nyu|new york university",ignore_case = T)),
                        description%>%
                          str_detect(regex("poli(tics|tical|sci|cy)",ignore_case = T))
                        )%>%
  select(user_id,screen_name,name,friends_count,description)
nyc.id=c(nyc.id,can.id)%>%unique() #already scrapped and in the list
if(nrow(user.dfx)==0){break}
user.df=rbind(user.df,user.dfx) #merge user info df
can.id=user.dfx$user_id #to be scrapped
rej.idx=useridx[!useridx%in%can.id] #not qualified
rej.id=c(rej.id,rej.idx)%>%unique()
acc.id=c(acc.id,can.id)%>%unique()
info.id=c(info.id,useridx)%>%unique()
edge.listx=user.following%>%filter(user_id%in%acc.id) #add edgelist
edge.list=rbind(edge.list,edge.listx)
}
```

## Draw the network

```{r,echo=TRUE}
load("friendship.rdata")
edge.list%>%head(5)
user.df%>%head(5)
library(igraph)
net=graph_from_data_frame(edge.list)
netsim=igraph::simplify(net, remove.multiple = T, remove.loops = F)
V(netsim)$id=V(netsim)$name

user.df=user.df %>%
  unique()%>%
    arrange(match(user_id, V(netsim)$id))
user.name=user.df%>%
  pull(name)
V(netsim)$name=user.name
V(netsim)$degree=user.df$friends_count
set.seed(123)
plot(netsim,vertex.name=V(netsim)$user.name,vertex.color="gold", vertex.size=log(V(netsim)$degree)*.8+0.01, 
     vertex.frame.color="gray", vertex.label.color="black", 
     vertex.label.cex=0.5, vertex.label.dist=2, edge.curved=0.5,edge.arrow.size=.2,vertex.label.cex=.5,vertex.label=NA)
```


## Other APIs

- `Rfacebook` (facebook) <https://cran.r-project.org/web/packages/Rfacebook/Rfacebook.pdf>

- `RedditExtractoR` (reddit) <https://cran.r-project.org/web/packages/RedditExtractoR/RedditExtractoR.pdf>

- `imdbapi` (IMDB) <https://cran.r-project.org/web/packages/imdbapi/imdbapi.pdf>

- `omdbapi`(The Open Movie Database) <https://github.com/hrbrmstr/omdbapi>


## API request directly from R

The movie database API <https://www.themoviedb.org/>

- Signup and request for an API key <https://developers.themoviedb.org/3/getting-started/introduction>

- Write functions to make query:
    
    - Create a query
    - From JSON file to dataframe
    
- Build your own network based on these functions

## preparation

```{r, echo=TRUE, message=FALSE, warning=FALSE}
#install.packages("rjson")
library(rjson)
#install.packages("jsonlite")
library(jsonlite)
```

## search people id

Search people based on the name:
<https://developers.themoviedb.org/3/search/search-people>

```{r,echo=TRUE,eval=FALSE}
### get actor/director id based on name
get_search_people = function(people,api="your-api-key"){
  
  search = URLencode(people, reserved = TRUE) 
  
  people_url = paste0("https://api.themoviedb.org/3/search/person?api_key=",api,"&language=en-US&query=",
                      search,"&include_adult=false")
  people_json = jsonlite::fromJSON(paste(readLines(people_url), collapse=""))
  
  total_page = people_json$total_pages
  if (total_page > 1){
    people_id_df = data.frame()
    n = min(5, total_page)
    for (j in 1:n){
      url = paste0("https://api.themoviedb.org/3/search/person?api_key=",api,"&language=en-US&query=",
                   search,"&page=",j,"&include_adult=false")
      json = jsonlite::fromJSON(paste(readLines(people_url), collapse=""))
      temp = json$results %>% as.data.frame() %>% select(id, name)
      people_id_df = rbind(people_id_df, temp)
    }
  } else {
    people_id_df = people_json$results %>% as.data.frame() %>% select(id, name)
  }
  
  return(people_id_df) # this dataframe only contains name and people id
  
}
actress="Julianne Moore" # She comes from NC
get_search_people(actress)
```

## search movies based on people id

Search the movies of one person based on id:<https://developers.themoviedb.org/3/people/get-person-movie-credits>


```{r,echo=TRUE,eval=FALSE}
# get movie details of one person with the person id
get_people_movie = function(id,api="your-api-key"){
  
  url = paste0("https://api.themoviedb.org/3/person/",id,"/movie_credits?api_key=",api,"&language=en-US")
  people_movie_json = jsonlite::fromJSON(paste(readLines(url), collapse=""))
  people_movie_df = people_movie_json$cast %>% as.data.frame() %>% select(character, poster_path, id, vote_average, original_language,
                                                                          title, popularity, overview, release_date)
  base_url = "http://image.tmdb.org/t/p/w500" 
  people_movie_df = people_movie_df %>% mutate(poster_path = paste0(base_url, poster_path))
  
  return(people_movie_df)
  
}
id=1231 # got from the previous function `get_search_people`
get_people_movie(id)
```


