---
title: "LAB6"
author: "YunranChen"
date: "2/19/2019"
output: 
  ioslides_presentation:
    widescreen: true
    smaller: true
---

<style>
slides > slide {
  overflow-x: auto !important;
  overflow-y: auto !important;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


## Outline

**Dataset available on the web (awesome):**

- <https://github.com/briatte/awesome-network-analysis> Papers, reviews, dataset, software (tutorial)
- Katherine's webpage <http://kateto.net/2016/05/network-datasets/>
- Kaggle <https://www.kaggle.com/datasets>
- dataworld <https://data.world/search?q=network+dataset>


**Web scraping:**

- Web APIs(application programming interface): website offers a set of structured http requests that return JSON or XML files. `rtweet`,`twitteR`,`Rfacebook`
- Screen scraping: extract data from source code of website, with html parser or regular expression matching. (lab 7)

**Twitter API**

## R package `rtweet`

Official website: <https://rtweet.info/index.html>

**Explore the official websites to find more info.**

- All the functions
- Tutorial
- FAQ (possible issues)

Good documentation; Recommended over another R package `twitteR`.

## Preparation

```{r install, echo=TRUE, message=FALSE, warning=FALSE}
#install.packages("rtweet")
library("rtweet")
```

## API authorization

Follow <https://rtweet.info/articles/auth.html>

- Create a Twitter App

- Authorization via access token:  `create_token()` automatically saves your token as an environment variable, you’ll be set for future sessions as well!

```{r,echo=TRUE, eval=FALSE}
#save your token as an environment variable for you
create_token(
  app = "your_research_app",
  consumer_key = "consumer_API_key",
  consumer_secret = "consumer_API_secret_key",
  access_token = "access_token",
  access_secret = "access_token_secret")
```

## `rtweet`

**API request**

- <https://developer.twitter.com/en/docs/tweets/search/api-reference/get-search-tweets>

- Send a request specifying parameters; Get response in JSON format

- `search_tweets`: **sampling** from tweets in past 7 days matching keywords (**specified # of tweets**)  -- recent/popular/mixed

- `stream_tweets`: sampling/keyword-filter/user-track/geo-location **live stream** for future time period;(**specified time period**) 

## `search_tweets`

- limiting searches to 10 keywords and operators

- only past 6-9 days of Tweets


**Parameters:**

`help()` or see <https://developer.twitter.com/en/docs/tweets/search/api-reference/get-search-tweets>

- `q`: Query to be searched. Spaces/AND -- both ("data science";"data AND science"); OR -- either or (data OR science); '""' -- exact ('"data science"'; "\"data science\""); "#datascience" -- track hashtag; "@duke" -- track at.

See operators: <https://developer.twitter.com/en/docs/tweets/rules-and-filtering/overview/standard-operators.html>

- `n`: total number of desired tweets. At most 18,000 in a single call; For $>$ 18,000, `retryonratelimit`=TRUE

- `type`: "recent","popular","mixed"

- `include_rts`: whether to include retweets

- `geocode`:  "latitude,longitude,radius" 

- `lang`: language

- `parse`: TRUE(dateframe); FALSE(list)

```{r,echo=TRUE,cache=TRUE}
rt <- search_tweets(
  q="#dukebasketball", #Query to be searched
  n = 10,
include_rts=FALSE,
result_type="recent",
geocode = "36.00,-78.94,5mi"
)
rt

rt <- search_tweets(
  "trump OR president", n = 10,
  lang = "en"
)
rt

search_tweets(
  q="#dukebasketball", #Query to be searched
  n = 10,
include_rts=FALSE,
result_type="recent",
geocode = "36.00,-78.94,5mi"
)
```

## `search_tweets`

- dataframe: each row a tweet

- `users_data`: only extract user-related column

- `ts_plot`

- `lat_lng`


```{r,echo=TRUE,cache=TRUE}
## search for 18000 tweets using the rstats hashtag
rt <- search_tweets(
  "#dukebasketball", n = 50000, include_rts = FALSE,
  geocode = "36.00,-78.94,2000mi"
)
rt_dmbb=rt
class(rt)

## preview tweets data
names(rt)


## preview users data
users_data(rt)%>%names()

## plot time series (if ggplot2 is installed)
ts_plot(rt) #Duke vs No. 16 Louisville
```

## `search_tweets2`

Search different queries independently. 

Other parameters are the same.

```{r,echo=TRUE,cache=TRUE}
st2 <- search_tweets2(
  c("\"data science\"", "rstats OR python"),
  n = 50
)
st2$query
names(st2)
```

## Visualization

`research_tweets` returns a dataframe. Visualization based on the dataframe.

- `ts_plot`: Creates a ggplot2 plot of the frequency of tweets over a specified interval of time. Using `ggplot2`; 

- Map: Using `lat_lng`

```{r,echo=TRUE}
## plot time series of tweets
ts_plot(rt_dmbb, "3 hours") + # a ggplot object
  ggplot2::theme_minimal() + # Add multiple layers directly
  ggplot2::theme(plot.title = ggplot2::element_text(face = "bold")) +
  ggplot2::labs(
    x = NULL, y = NULL,
    title = "Frequency of #dukebasketball Twitter statuses from past 6-9 days",
    subtitle = "Twitter status (tweet) counts aggregated using three-hour intervals",
    caption = "\nSource: Data collected from Twitter's REST API via rtweet"
  )
# an example using `groupby` with ggplot2
ts_plot(rt_dmbb%>%dplyr::group_by(is_quote), "3 hours") + # a ggplot object
  ggplot2::theme_minimal()
```

```{r,echo=TRUE}
#install.packages("maps")
## create lat/lng variables using all available tweet and profile geo-location data
rt_dmbbll <- lat_lng(rt_dmbb)
names(rt_dmbbll)[!names(rt_dmbbll)%in%names(rt_dmbb)]

## plot state boundaries
par(mar = c(0, 0, 0, 0))
maps::map("state","north carolina", lwd = .25)

## plot lat and lng points onto state map
with(rt_dmbbll, points(lng, lat, pch = 20, cex = .75, col = rgb(0, .3, .7, .75)))
```

## `stream_tweets`

<https://developer.twitter.com/en/docs/tweets/search/api-reference/get-search-tweets>

- `q`

    - Sampling a small random sample of all publicly available tweets `q=""`

    - Filtering via a search-like query (up to 400 keywords) `q="duke,basketball"`. "," separation

    - Tracking via vector of user ids (up to 5000 user_ids) `q="hillaryclinton,realdonaldtrump"`. "," separation

    - Location via geo coordinates (1-360 degree location boxes) `q=c(-125, 26, -65, 49)`

- `timeout` : amount of time (seconds) **occupy your r session**

- `parse`: TRUE(dataframe); FALSE(JSON).

- `file_name`: save as a file

**Usually the file is large. Recommend to save as JSON file then parse to data.frame.**

To ensure the stream automatically reconnects following any interruption prior to the specified stream time, use `stream_tweets2()`.

```{r,echo=TRUE,cache=TRUE}
## Randomly sample (approximately 1%) from the live stream of all tweets for 30 seconds (default)
rt <- stream_tweets("")
nrow(rt)

rt <- stream_tweets("duke,bluedevil,unc")
nrow(rt)
rt
## stream tweets for a day (60 secs x 60 mins * 24 hours )
stream_tweets(
  "abc,nbcnews,cbsnews,nytimes,bbcworld,bbcbreaking,bbcnews,bbcsport",
  timeout = 60*2,
  file_name = "tweetsth1.json",
  parse = FALSE
)

## read in the data as a tidy tbl data frame
djt1 <- parse_stream("tweetsth1.json")
djt1
```

## Other functions

<https://rtweet.info/reference/index.html>

# Examples on creating networks

## Preparation

```{r,echo=TRUE}
library(dplyr)
library(igraph)
library(purrr)
```

## Creating networks based on datasets

Retweet networks

directed: retweet

Similarly, we can get quote networks, replying networks.

```{r,echo=TRUE,cache=TRUE}
rt_duke <- search_tweets(
  "#duke", n = 1000
)
nrow(rt_duke)
names(rt_duke)

netdf=rt_duke%>%dplyr::select(.,screen_name,retweet_screen_name,is_retweet)
netdfr=netdf%>%filter(is_retweet)%>%select(-is_retweet)
netdfp=netdf%>%filter(!is_retweet)%>%pull(screen_name)
igra_duke=graph_from_data_frame(netdfr)#+netdfp
E(igra_duke)$weight=rep(1,ecount(igra_duke))
igra_duke_s <- igraph::simplify( igra_duke, remove.multiple = T, remove.loops = F, 
                 edge.attr.comb=c(weight="sum"))
igra_duke_s
plot(igra_duke_s,vertex.color="gold", vertex.size=log(degree(igra_duke_s))*3+1, 
     vertex.frame.color="gray", vertex.label.color="black", 
     vertex.label.cex=log(degree(igra_duke_s))*0.2+0.1, vertex.label.dist=2, edge.curved=0.5,edge.arrow.size=.2)
```

Friendship networks

directed: following

`get_friends()`: Get user IDs of accounts followed by target user(s).

```{r,echo=TRUE,cache=TRUE}
rt_dukembb <- search_tweets(
  "#dukebasketball", n = 1000
)

names(rt_dukembb)

users=rt_dukembb$user_id%>%unique()

##maximum ids: 100
abc=get_friends(users[1:5],n=100,retryonratelimit = TRUE)
abc%>%filter(user_id%in%users)

```

What if more than 100 ids?

```{r,echo=TRUE,cache=TRUE,eval=FALSE}
for (i in --){
  mat=get_friends(users[--])%>%filter(user_id%in%users)
  limit <- rate_limit("get_friends")
  if (--){
    Sys.sleep(--)
  }
}
```

## `rate_limit`

<https://developer.twitter.com/en/docs/developer-utilities/rate-limit-status/api-reference/get-application-rate_limit_status>

```{r,echo=TRUE}
rate_limit()%>%head()
rate_limit("get_friends")
```

```{r,echo=TRUE,cache=TRUE,eval=FALSE}
for (i in --){
  mat=get_friends(users[--])%>%filter(user_id%in%users)
  limit <- rate_limit("get_friends")
  if (limit$remaining==0){
    Sys.sleep(60)
  }
}
```



